---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# eHDPrep

<!-- badges: start -->
[![Downloads](https://cranlogs.r-pkg.org/badges/grand-total/eHDPrep)](https://cranlogs.r-pkg.org/badges/grand-total/eHDPrep)
[![CRAN status](https://www.r-pkg.org/badges/version/eHDPrep)](https://cran.r-project.org/package=eHDPrep)
[![R-CMD-check](https://github.com/overton-group/eHDPrep/actions/workflows/r.yml/badge.svg)](https://github.com/overton-group/eHDPrep/actions/workflows/r.yml/badge.svg)
<!-- badges: end -->

The goal of 'eHDPrep' is to provide robust quality control and semantic enrichment tools for preparation of health datasets. High-level and low-level functionality are included for general and specialist 'R' users, respectively. A detailed vignette can be accessed using: `vignette("Introduction_to_eHDPrep", package = "eHDPrep")`.

## Installation

You can install the released version of 'eHDPrep' from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("eHDPrep")
```

Or from [GitHub](https://github.com) with:

``` r
install.packages("devtools")
devtools::install_github("overton-group/eHDPrep")
```

## Example

'eHDPrep' can prepare health data for analysis with several approaches. For example, standardising strings representing missing values to `NA`:

```{r example}
library(eHDPrep)
data("example_data")

# original values in t_stage variable
unique(example_data$t_stage)

# predefined value "equivocal" is removed
unique(eHDPrep::strings_to_NA(example_data, strings_to_replace = "equivocal")$t_stage)


```

## System Requirements

Some additional system dependencies are required for 'eHDPrep'. These are detailed below:

### Ubuntu

```{r ubuntu-req}
remotes::system_requirements(".", os = "ubuntu", os_release = "18.04")
remotes::system_requirements(".", os = "ubuntu", os_release = "20.04")
```

### Opensuse

```{r opensuse-req}
remotes::system_requirements(".", os = "opensuse", os_release = "42.3")
```

### CentOS

```{r centos-req}
remotes::system_requirements(".", os = "centos", os_release = "7")
remotes::system_requirements(".", os = "centos", os_release = "8")
```

### Red Hat

```{r redhat-req}
remotes::system_requirements(".", os = "redhat", os_release = "7")
remotes::system_requirements(".", os = "redhat", os_release = "8")
```
